---
title: "Figure3"
author: "Andrew Dominguez"
date: "7/30/2020"
output: html_document
---

```{r}
setwd("~/Manuscript.Figures")
```


```{r}
otu = read.table(file="../Data/FungiAD.otu_table.txt", header=T, sep='\t',row.names = 1)
head(otu)
dim(otu)

tax <- read.table(file="../Data/FungiAD.ASVs.taxonomy.fix.txt", sep='\t', header=TRUE,row.names = 1)
head(tax)

dim(tax)

taxmat <- as(tax,"matrix")
head(taxmat)

TAX = tax_table(taxmat)

otumat <- as(as.matrix(otu), "matrix")
mode(otumat) <- "numeric"
OTU = otu_table(otumat, taxa_are_rows = TRUE)

otumat

meta0 = read.table("../Data/Andrew_ITS.mapping_file.txt",
                  header=TRUE,row.names=1,
                  sep="\t",stringsAsFactors=FALSE)
meta0

sampleData <- sample_data(meta0)


physeq = phyloseq(OTU,TAX,sampleData)



physeq


physeq.prune = prune_taxa(taxa_sums(physeq) > 0, physeq)
physeq

readcount = data.table(as(sample_data(physeq.prune), "data.frame"),
                 TotalReads = sample_sums(physeq.prune), 
                 keep.rownames = TRUE)
setnames(readcount, "rn", "SampleID")


readcount = readcount[order(readcount$TotalReads), c("SampleID", "TotalReads")]
head(readcount)

set.seed(711)
physeq.prune.rarefy = rarefy_even_depth(physeq.prune, sample.size = 4941, replace = FALSE, trimOTUs = TRUE)
physeq.prune.rarefy

physeq.prune.rarefy.fun <- subset_taxa(physeq.prune.rarefy,Kingdom == "Fungi")
physeq.prune.rarefy.fun

fun.con <- subset_samples(physeq.prune.rarefy.fun, Treatment == "Control")
fun.june <- subset_samples(physeq.prune.rarefy.fun, Date == "June_2017")
fun.nov <- subset_samples(physeq.prune.rarefy.fun, Date == "November_2017")
fun.june.control <- subset_samples(fun.june, Treatment == "Control")
fun.nov.control <- subset_samples(fun.nov, Treatment == "Control")
fun.june.erle <- subset_samples(fun.june, Grass == "ERLE")
fun.june.boer <- subset_samples(fun.june, Grass == "BOER")
fun.nov.erle <- subset_samples(fun.nov, Grass == "ERLE")
fun.nov.boer <- subset_samples(fun.nov, Grass == "BOER")
```


####group classes with less than 1% representation into one category - Erle June

##Make taxonomy table into a matrix
```{r}
tax.fun.erle.j <- as(tax_table(fun.june.erle),"matrix")
head(tax.fun.erle.j)
```

##Relabel NA as Unknown

```{r}
tax.fun.erle.j[is.na(tax.fun.erle.j)] <- "Unknown"
head(tax.fun.erle.j)
```

###Convert tax table back to phyloseq object and generate phyloseq object with new tax table
```{r}
TAX.fun.erle.j <- tax_table(tax.fun.erle.j)
```

```{r}
fun.erle.j2 <- phyloseq(sample_data(fun.june.erle),otu_table(fun.june.erle),TAX.fun.erle.j)
fun.erle.j2
```

```{r}
fun.june.erle0 = transform_sample_counts(fun.erle.j2, 
                                                      function(x) x / sum(x))
```

```{r}
glom.fun.erle2j <- tax_glom(fun.june.erle0,taxrank = 'Class')
data_glom.fun.erle2j <- psmelt(glom.fun.erle2j)
data_glom.fun.erle2j$Class <- as.character(data_glom.fun.erle2j$Class)
```

```{r}
unique((data_glom.fun.erle2j$Class))
```

Top 6 classes
```{r}
data_glom.fun.june.erle2.top6 <- subset(data_glom.fun.erle2j, Class == "Dothideomycetes"  | Class ==  "Agaricomycetes"  | Class ==   "Eurotiomycetes"   | Class ==  "Sordariomycetes" | Class ==  
   "Pezizomycetes"  | Class ==   "Lecanoromycetes"  )
```

```{r}
unique((data_glom.fun.june.erle2.top6$Class))
```

```{r}
fun.june.erle <- ggplot(data_glom.fun.june.erle2.top6,aes(Treatment,Abundance,color=Class)) + geom_boxplot() +
  scale_color_manual(values = c("indianred1", "lightsalmon","grey26","lightgreen", "lightblue1", "royalblue3")) + 
  theme_bw(base_size = 20) + labs(y= "Relative Abundance", x = "") + 
  ggtitle("A) ERLE Pre monsoon") # + theme(axis.text.x = element_text(angle = 90))
```

```{r}
fun.june.erle
```

#Stats comparing phylum abundance between treatments - Lovegrass June

```{r}
unique((data_glom.fun.erle2j$Class))
```

```{r}
Dothideomycetes <- subset(data_glom.fun.erle2j, Class == "Dothideomycetes")
Agaricomycetes <- subset(data_glom.fun.erle2j, Class == "Agaricomycetes")
Eurotiomycetes <- subset(data_glom.fun.erle2j, Class == "Eurotiomycetes")
Sordariomycetes <- subset(data_glom.fun.erle2j, Class == "Sordariomycetes")
Pezizomycetes <- subset(data_glom.fun.erle2j, Class == "Pezizomycetes")
Lecanoromycetes <- subset(data_glom.fun.erle2j, Class == "Lecanoromycetes")
```

```{r}
Dothideomycetes$Treatment <- as.factor(Dothideomycetes$Treatment)
Agaricomycetes$Treatment <- as.factor(Agaricomycetes$Treatment)
Eurotiomycetes$Treatment <- as.factor(Eurotiomycetes$Treatment)
Sordariomycetes$Treatment <- as.factor(Sordariomycetes$Treatment)
Pezizomycetes$Treatment <- as.factor(Pezizomycetes$Treatment)
Lecanoromycetes$Treatment <- as.factor(Lecanoromycetes$Treatment)
```


```{r}
kw.1 <- kruskal.test(Abundance ~ Treatment,data = Dothideomycetes)
kw.1
kw.2 <-kruskal.test(Abundance ~ Treatment,data = Agaricomycetes)
kw.2
kw.3 <- kruskal.test(Abundance ~ Treatment,data = Eurotiomycetes)
kw.3
kw.4 <- kruskal.test(Abundance ~ Treatment,data = Sordariomycetes)
kw.4
kw.5 <- kruskal.test(Abundance ~ Treatment,data = Pezizomycetes)
kw.5
kw.6 <- kruskal.test(Abundance ~ Treatment,data = Lecanoromycetes)
kw.6
```


####group classes with less than 1% representation into one category - Erle November

##Make taxonomy table into a matrix
```{r}
tax.fun.erle.n <- as(tax_table(fun.nov.erle),"matrix")
head(tax.fun.erle.n)
```

##Relabel NA as Unknown

```{r}
tax.fun.erle.n[is.na(tax.fun.erle.n)] <- "Unknown"
head(tax.fun.erle.n)
```

###Convert tax table back to phyloseq object and generate phyloseq object with new tax table
```{r}
TAX.fun.erle.n <- tax_table(tax.fun.erle.n)
```

```{r}
fun.erle.n2 <- phyloseq(sample_data(fun.nov.erle),otu_table(fun.nov.erle),TAX.fun.erle.n)
fun.erle.n2
```

```{r}
fun.june.erle0n = transform_sample_counts(fun.erle.n2, 
                                                      function(x) x / sum(x))
```

```{r}
glom.fun.erle2n <- tax_glom(fun.june.erle0n,taxrank = 'Class')
data_glom.fun.erle2n <- psmelt(glom.fun.erle2n)
data_glom.fun.erle2n$Class <- as.character(data_glom.fun.erle2n$Class)
```

```{r}
unique((data_glom.fun.erle2n$Class))
```

Top 6 classes
```{r}
data_glom.fun.nov.erle2.top6 <- subset(data_glom.fun.erle2n, Class == "Dothideomycetes"  | Class ==  "Eurotiomycetes"  | Class ==   "Sordariomycetes"   | Class ==  "Pezizomycetes" | Class ==  
   "Agaricomycetes"  | Class ==   "Tremellomycetes"  )
```

```{r}
unique((data_glom.fun.nov.erle2.top6$Class))
```

```{r}
fun.nov.erle <- ggplot(data_glom.fun.nov.erle2.top6,aes(Treatment,Abundance,color=Class)) + geom_boxplot() +
  scale_color_manual(values = c("indianred1", "lightsalmon","gray26","lightgreen", "lightblue1", "royalblue3")) + 
  theme_bw(base_size = 20) + labs(y= "", x = "") + 
  ggtitle("B) ERLE Post monsoon")
```

```{r}
fun.nov.erle
```

```{r}
Pre_Post_Fun.erle.plot = ggarrange(fun.june.erle, fun.nov.erle, ncol=2, common.legend = TRUE, legend = "right")#, labels = c("A", "B"))
Pre_Post_Fun.erle.plot
```

#Stats comparing phylum abundance between treatments - Lovegrass November

```{r}
unique((data_glom.fun.erle2n$Class))
```

```{r}
Dothideomycetes <- subset(data_glom.fun.erle2n, Class == "Dothideomycetes")
Eurotiomycetes <- subset(data_glom.fun.erle2n, Class == "Eurotiomycetes")
Sordariomycetes <- subset(data_glom.fun.erle2n, Class == "Sordariomycetes")
Pezizomycetes <- subset(data_glom.fun.erle2n, Class == "Pezizomycetes")
Agaricomycetes <- subset(data_glom.fun.erle2n, Class == "Agaricomycetes")
Tremellomycetes <- subset(data_glom.fun.erle2n, Class == "Tremellomycetes")
```

```{r}
Dothideomycetes$Treatment <- as.factor(Dothideomycetes$Treatment)
Eurotiomycetes$Treatment <- as.factor(Eurotiomycetes$Treatment)
Sordariomycetes$Treatment <- as.factor(Sordariomycetes$Treatment)
Pezizomycetes$Treatment <- as.factor(Pezizomycetes$Treatment)
Agaricomycetes$Treatment <- as.factor(Agaricomycetes$Treatment)
Tremellomycetes$Treatment <- as.factor(Tremellomycetes$Treatment)
```


```{r}
kw.1 <- kruskal.test(Abundance ~ Treatment,data = Dothideomycetes)
kw.1
kw.2 <-kruskal.test(Abundance ~ Treatment,data = Eurotiomycetes)
kw.2
kw.3 <- kruskal.test(Abundance ~ Treatment,data = Sordariomycetes)
kw.3
kw.4 <- kruskal.test(Abundance ~ Treatment,data = Pezizomycetes)
kw.4
kw.5 <- kruskal.test(Abundance ~ Treatment,data = Agaricomycetes)
kw.5
kw.6 <- kruskal.test(Abundance ~ Treatment,data = Tremellomycetes)
kw.6
```


####group classes with less than 1% representation into one category - Boer June

##Make taxonomy table into a matrix
```{r}
tax.fun.boer.j <- as(tax_table(fun.june.boer),"matrix")
head(tax.fun.boer.j)
```

##Relabel NA as Unknown

```{r}
tax.fun.boer.j[is.na(tax.fun.boer.j)] <- "Unknown"
head(tax.fun.boer.j)
```

###Convert tax table back to phyloseq object and generate phyloseq object with new tax table
```{r}
TAX.fun.boer.j <- tax_table(tax.fun.boer.j)
```

```{r}
fun.boer.j2 <- phyloseq(sample_data(fun.june.boer),otu_table(fun.june.boer),TAX.fun.boer.j)
fun.boer.j2
```

```{r}
fun.june.boer0 = transform_sample_counts(fun.boer.j2, 
                                                      function(x) x / sum(x))
```

```{r}
glom.fun.boer2j <- tax_glom(fun.june.boer0,taxrank = 'Class')
data_glom.fun.boer2j <- psmelt(glom.fun.boer2j)
data_glom.fun.boer2j$Class <- as.character(data_glom.fun.boer2j$Class)
```

```{r}
unique((data_glom.fun.boer2j$Class))
```

Top 6 classes
```{r}
data_glom.fun.june.boer2.top6 <- subset(data_glom.fun.boer2j, Class == "Dothideomycetes"  | Class ==  "Agaricomycetes"  | Class ==   "Pezizomycetes"   | Class ==  "Eurotiomycetes" | Class ==  
   "Sordariomycetes"  | Class ==   "Leotiomycetes"  )
```

```{r}
unique((data_glom.fun.june.boer2.top6$Class))
```

```{r}
fun.june.boer <- ggplot(data_glom.fun.june.boer2.top6,aes(Treatment,Abundance,color=Class)) + geom_boxplot() +
  scale_color_manual(values = c("indianred1", "lightsalmon","gray26","lightgreen", "lightblue1", "royalblue3")) + 
  theme_bw(base_size = 20) + 
  labs(y= "Relative Abundance", x = "") + 
  ggtitle("C) BOER Pre monsoon")
```

```{r}
fun.june.boer
```

#Stats comparing phylum abundance between treatments - black grama June

```{r}
unique((data_glom.fun.boer2j$Class))
```

```{r}
Dothideomycetes.june <- subset(data_glom.fun.boer2j, Class == "Dothideomycetes")
Agaricomycetes.june <- subset(data_glom.fun.boer2j, Class == "Agaricomycetes")
Pezizomycetes.june <- subset(data_glom.fun.boer2j, Class == "Pezizomycetes")
Eurotiomycetes.june <- subset(data_glom.fun.boer2j, Class == "Eurotiomycetes")
Sordariomycetes.june <- subset(data_glom.fun.boer2j, Class == "Sordariomycetes")
Leotiomycetes.june <- subset(data_glom.fun.boer2j, Class == "Leotiomycetes")
```

```{r}
Dothideomycetes.june$Treatment <- as.factor(Dothideomycetes.june$Treatment)
Agaricomycetes.june$Treatment <- as.factor(Agaricomycetes.june$Treatment)
Pezizomycetes.june$Treatment <- as.factor(Pezizomycetes.june$Treatment)
Eurotiomycetes.june$Treatment <- as.factor(Eurotiomycetes.june$Treatment)
Sordariomycetes.june$Treatment <- as.factor(Sordariomycetes.june$Treatment)
Leotiomycetes.june$Treatment <- as.factor(Leotiomycetes.june$Treatment)
```


```{r}
kw.1 <- kruskal.test(Abundance ~ Treatment,data = Dothideomycetes.june)
kw.1
kw.2 <-kruskal.test(Abundance ~ Treatment,data = Agaricomycetes.june)
kw.2
kw.3 <- kruskal.test(Abundance ~ Treatment,data = Pezizomycetes.june)
kw.3
kw.4 <- kruskal.test(Abundance ~ Treatment,data = Eurotiomycetes.june)
kw.4
kw.5 <- kruskal.test(Abundance ~ Treatment,data = Sordariomycetes.june)
kw.5
kw.6 <- kruskal.test(Abundance ~ Treatment,data = Leotiomycetes.june)
kw.6
```


####group classes with less than 1% representation into one category - boer November

##Make taxonomy table into a matrix
```{r}
tax.fun.boer.n <- as(tax_table(fun.nov.boer),"matrix")
head(tax.fun.boer.n)
```

##Relabel NA as Unknown

```{r}
tax.fun.boer.n[is.na(tax.fun.boer.n)] <- "Unknown"
head(tax.fun.boer.n)
```

###Convert tax table back to phyloseq object and generate phyloseq object with new tax table
```{r}
TAX.fun.boer.n <- tax_table(tax.fun.boer.n)
```

```{r}
fun.boer.n2 <- phyloseq(sample_data(fun.nov.boer),otu_table(fun.nov.boer),TAX.fun.boer.n)
fun.boer.n2
```

```{r}
fun.june.boer0n = transform_sample_counts(fun.boer.n2, 
                                                      function(x) x / sum(x))
```

```{r}
glom.fun.boer2n <- tax_glom(fun.june.boer0n,taxrank = 'Class')
data_glom.fun.boer2n <- psmelt(glom.fun.boer2n)
data_glom.fun.boer2n$Class <- as.character(data_glom.fun.boer2n$Class)
```

```{r}
unique((data_glom.fun.boer2n$Class))
```

Top 6 classes
```{r}
data_glom.fun.nov.boer2.top6 <- subset(data_glom.fun.boer2n, Class == "Dothideomycetes"  | Class ==  "Agaricomycetes"  | Class ==   "Pezizomycetes"   | Class ==  "Sordariomycetes" | Class ==  
  "Eurotiomycetes"  | Class ==   "Leotiomycetes"  )
```

```{r}
unique((data_glom.fun.nov.boer2.top6$Class))
```

```{r}
fun.nov.boer <- ggplot(data_glom.fun.nov.boer2.top6,aes(Treatment,Abundance,color=Class)) + geom_boxplot() +
  scale_color_manual(values = c("indianred1", "lightsalmon","gray26","lightgreen", "lightblue1", "royalblue3")) + theme_bw(base_size = 20) + 
  labs(y= "", x = "") + 
  ggtitle("D) BOER Pre monsoon")
```

```{r}
fun.nov.boer
```

```{r}
Pre_Post_Fun.treatment.plot = ggarrange(fun.june.boer, fun.nov.boer, ncol=2, common.legend = TRUE, legend = "right")#, labels = c("C", "D"))
Pre_Post_Fun.treatment.plot
```

#Create figure3

```{r}
figure_3 = ggarrange(Pre_Post_Fun.erle.plot, Pre_Post_Fun.treatment.plot, nrow = 2)
figure_3
```

##Save figure 2

```{r warning=FALSE}
pdf("../Figures/Figure_3_Pre_Post.pdf", width = 12, height = 10 )
figure_3
dev.off()
```


```{r}
#figure3 <- ggarrange(fun.june.erle, fun.nov.erle, fun.june.boer, fun.nov.boer,
#                    labels = c("A", "B","C","D"),
#                    ncol = 2, nrow = 2)
```

```{r}
#figure3
```

```{r}
#figure3
#ggsave("Figure3.png",width=12,height=8,dpi = 400)
```

#Stats comparing phylum abundance between treatments - black grama November

```{r}
unique((data_glom.fun.boer2n$Class))
```

```{r}
Dothideomycetes.nov <- subset(data_glom.fun.boer2n, Class == "Dothideomycetes")
Agaricomycetes.nov <- subset(data_glom.fun.boer2n, Class == "Agaricomycetes")
Pezizomycetes.nov <- subset(data_glom.fun.boer2n, Class == "Pezizomycetes")
Sordariomycetes.nov <- subset(data_glom.fun.boer2n, Class == "Sordariomycetes")
Eurotiomycetes.nov <- subset(data_glom.fun.boer2n, Class == "Eurotiomycetes")
Lecanoromycetes.nov <- subset(data_glom.fun.boer2n, Class == "Lecanoromycetes")
```

```{r}
Dothideomycetes.nov$Treatment <- as.factor(Dothideomycetes.nov$Treatment)
Agaricomycetes.nov$Treatment <- as.factor(Agaricomycetes.nov$Treatment)
Pezizomycetes.nov$Treatment <- as.factor(Pezizomycetes.nov$Treatment)
Sordariomycetes.nov$Treatment <- as.factor(Sordariomycetes.nov$Treatment)
Eurotiomycetes.nov$Treatment <- as.factor(Eurotiomycetes.nov$Treatment)
Lecanoromycetes.nov$Treatment <- as.factor(Lecanoromycetes.nov$Treatment)
```


```{r}
kw.1 <- kruskal.test(Abundance ~ Treatment,data = Dothideomycetes.nov)
kw.1
kw.2 <-kruskal.test(Abundance ~ Treatment,data = Agaricomycetes.nov)
kw.2
kw.3 <- kruskal.test(Abundance ~ Treatment,data = Pezizomycetes.nov)
kw.3
kw.4 <- kruskal.test(Abundance ~ Treatment,data = Sordariomycetes.nov)
kw.4
kw.5 <- kruskal.test(Abundance ~ Treatment,data = Eurotiomycetes.nov)
kw.5
kw.6 <- kruskal.test(Abundance ~ Treatment,data = Lecanoromycetes.nov)
kw.6
```


