---
title: "Figure3"
author: "Andrew Dominguez"
date: "7/30/2020"
output: html_document
---

```{r}
setwd("~/Manuscript.Figures")
```


```{r}
otu = read.table(file="files/FungiAD.otu_table.txt", header=T, sep='\t',row.names = 1)
head(otu)
dim(otu)

tax <- read.table(file="files/FungiAD.ASVs.taxonomy.fix.txt", sep='\t', header=TRUE,row.names = 1)
head(tax)

dim(tax)

taxmat <- as(tax,"matrix")
head(taxmat)

TAX = tax_table(taxmat)

otumat <- as(as.matrix(otu), "matrix")
mode(otumat) <- "numeric"
OTU = otu_table(otumat, taxa_are_rows = TRUE)

otumat

meta0 = read.table("files/Andrew_ITS.mapping_file.txt",
                  header=TRUE,row.names=1,
                  sep="\t",stringsAsFactors=FALSE)
meta0

sampleData <- sample_data(meta0)


physeq = phyloseq(OTU,TAX,sampleData)



physeq


physeq.prune = prune_taxa(taxa_sums(physeq) > 0, physeq)
physeq

readcount = data.table(as(sample_data(physeq.prune), "data.frame"),
                 TotalReads = sample_sums(physeq.prune), 
                 keep.rownames = TRUE)
setnames(readcount, "rn", "SampleID")


readcount = readcount[order(readcount$TotalReads), c("SampleID", "TotalReads")]
head(readcount)

set.seed(711)
physeq.prune.rarefy = rarefy_even_depth(physeq.prune, sample.size = 4941, replace = FALSE, trimOTUs = TRUE)
physeq.prune.rarefy

physeq.prune.rarefy.fun <- subset_taxa(physeq.prune.rarefy,Kingdom == "Fungi")
physeq.prune.rarefy.fun

fun.con <- subset_samples(physeq.prune.rarefy.fun, Treatment == "Control")
fun.june <- subset_samples(physeq.prune.rarefy.fun, Date == "June_2017")
fun.nov <- subset_samples(physeq.prune.rarefy.fun, Date == "November_2017")
fun.june.control <- subset_samples(fun.june, Treatment == "Control")
fun.nov.control <- subset_samples(fun.nov, Treatment == "Control")
fun.june.erle <- subset_samples(fun.june, Grass == "ERLE")
fun.june.boer <- subset_samples(fun.june, Grass == "BOER")
fun.nov.erle <- subset_samples(fun.nov, Grass == "ERLE")
fun.nov.boer <- subset_samples(fun.nov, Grass == "BOER")
```


####group classes with less than 1% representation into one category - Erle June

##Make taxonomy table into a matrix
```{r}
tax.fun.erle.j <- as(tax_table(fun.june.erle),"matrix")
head(tax.fun.erle.j)
```

##Relabel NA as Unknown

```{r}
tax.fun.erle.j[is.na(tax.fun.erle.j)] <- "Unknown"
head(tax.fun.erle.j)
```

###Convert tax table back to phyloseq object and generate phyloseq object with new tax table
```{r}
TAX.fun.erle.j <- tax_table(tax.fun.erle.j)
```

```{r}
fun.erle.j2 <- phyloseq(sample_data(fun.june.erle),otu_table(fun.june.erle),TAX.fun.erle.j)
fun.erle.j2
```

```{r}
fun.june.erle0 = transform_sample_counts(fun.erle.j2, 
                                                      function(x) x / sum(x))
```

```{r}
glom.fun.erle2j <- tax_glom(fun.june.erle0,taxrank = 'Class')
data_glom.fun.erle2j <- psmelt(glom.fun.erle2j)
data_glom.fun.erle2j$Class <- as.character(data_glom.fun.erle2j$Class)
```

```{r}
unique((data_glom.fun.erle2j$Class))
```

Top 6 classes
```{r}
data_glom.fun.june.erle2.top6 <- subset(data_glom.fun.erle2j, Class == "Dothideomycetes"  | Class ==  "Agaricomycetes"  | Class ==   "Eurotiomycetes"   | Class ==  "Sordariomycetes" | Class ==  
   "Pezizomycetes"  | Class ==   "Lecanoromycetes"  )
```

```{r}
unique((data_glom.fun.june.erle2.top6$Class))
```

```{r}
fun.june.erle <- ggplot(data_glom.fun.june.erle2.top6,aes(Treatment,Abundance,color=Class)) + geom_boxplot() +
  scale_color_manual(values = c("indianred1", "lightsalmon","grey26","lightgreen", "lightblue1", "royalblue3")) + labs(y= "Relative Abundance") + theme_bw(base_size = 20) + theme(axis.text.x = element_text(angle = 90))
```

```{r}
fun.june.erle
```


####group classes with less than 1% representation into one category - Erle November

##Make taxonomy table into a matrix
```{r}
tax.fun.erle.n <- as(tax_table(fun.nov.erle),"matrix")
head(tax.fun.erle.n)
```

##Relabel NA as Unknown

```{r}
tax.fun.erle.n[is.na(tax.fun.erle.n)] <- "Unknown"
head(tax.fun.erle.n)
```

###Convert tax table back to phyloseq object and generate phyloseq object with new tax table
```{r}
TAX.fun.erle.n <- tax_table(tax.fun.erle.n)
```

```{r}
fun.erle.n2 <- phyloseq(sample_data(fun.nov.erle),otu_table(fun.nov.erle),TAX.fun.erle.n)
fun.erle.n2
```

```{r}
fun.june.erle0n = transform_sample_counts(fun.erle.n2, 
                                                      function(x) x / sum(x))
```

```{r}
glom.fun.erle2n <- tax_glom(fun.june.erle0n,taxrank = 'Class')
data_glom.fun.erle2n <- psmelt(glom.fun.erle2n)
data_glom.fun.erle2n$Class <- as.character(data_glom.fun.erle2n$Class)
```

```{r}
unique((data_glom.fun.erle2n$Class))
```

Top 6 classes
```{r}
data_glom.fun.nov.erle2.top6 <- subset(data_glom.fun.erle2n, Class == "Dothideomycetes"  | Class ==  "Eurotiomycetes"  | Class ==   "Sordariomycetes"   | Class ==  "Pezizomycetes" | Class ==  
   "Agaricomycetes"  | Class ==   "Tremellomycetes"  )
```

```{r}
unique((data_glom.fun.nov.erle2.top6$Class))
```

```{r}
fun.nov.erle <- ggplot(data_glom.fun.nov.erle2.top6,aes(Treatment,Abundance,color=Class)) + geom_boxplot() +
  scale_color_manual(values = c("indianred1", "lightsalmon","gray26","lightgreen", "lightblue1", "royalblue3")) + labs(y= "Relative Abundance") + theme_bw(base_size = 20) + theme(axis.text.x = element_text(angle = 90))
```

```{r}
fun.nov.erle
```


####group classes with less than 1% representation into one category - Boer June

##Make taxonomy table into a matrix
```{r}
tax.fun.boer.j <- as(tax_table(fun.june.boer),"matrix")
head(tax.fun.boer.j)
```

##Relabel NA as Unknown

```{r}
tax.fun.boer.j[is.na(tax.fun.boer.j)] <- "Unknown"
head(tax.fun.boer.j)
```

###Convert tax table back to phyloseq object and generate phyloseq object with new tax table
```{r}
TAX.fun.boer.j <- tax_table(tax.fun.boer.j)
```

```{r}
fun.boer.j2 <- phyloseq(sample_data(fun.june.boer),otu_table(fun.june.boer),TAX.fun.boer.j)
fun.boer.j2
```

```{r}
fun.june.boer0 = transform_sample_counts(fun.boer.j2, 
                                                      function(x) x / sum(x))
```

```{r}
glom.fun.boer2j <- tax_glom(fun.june.boer0,taxrank = 'Class')
data_glom.fun.boer2j <- psmelt(glom.fun.boer2j)
data_glom.fun.boer2j$Class <- as.character(data_glom.fun.boer2j$Class)
```

```{r}
unique((data_glom.fun.boer2j$Class))
```

Top 6 classes
```{r}
data_glom.fun.june.boer2.top6 <- subset(data_glom.fun.boer2j, Class == "Dothideomycetes"  | Class ==  "Agaricomycetes"  | Class ==   "Pezizomycetes"   | Class ==  "Eurotiomycetes" | Class ==  
   "Sordariomycetes"  | Class ==   "Leotiomycetes"  )
```

```{r}
unique((data_glom.fun.june.boer2.top6$Class))
```

```{r}
fun.june.boer <- ggplot(data_glom.fun.june.boer2.top6,aes(Treatment,Abundance,color=Class)) + geom_boxplot() +
  scale_color_manual(values = c("indianred1", "lightsalmon","gray26","lightgreen", "lightblue1", "royalblue3")) + labs(y= "Relative Abundance") + theme_bw(base_size = 20) + theme(axis.text.x = element_text(angle = 90))
```

```{r}
fun.june.boer
```


####group classes with less than 1% representation into one category - boer November

##Make taxonomy table into a matrix
```{r}
tax.fun.boer.n <- as(tax_table(fun.nov.boer),"matrix")
head(tax.fun.boer.n)
```

##Relabel NA as Unknown

```{r}
tax.fun.boer.n[is.na(tax.fun.boer.n)] <- "Unknown"
head(tax.fun.boer.n)
```

###Convert tax table back to phyloseq object and generate phyloseq object with new tax table
```{r}
TAX.fun.boer.n <- tax_table(tax.fun.boer.n)
```

```{r}
fun.boer.n2 <- phyloseq(sample_data(fun.nov.boer),otu_table(fun.nov.boer),TAX.fun.boer.n)
fun.boer.n2
```

```{r}
fun.june.boer0n = transform_sample_counts(fun.boer.n2, 
                                                      function(x) x / sum(x))
```

```{r}
glom.fun.boer2n <- tax_glom(fun.june.boer0n,taxrank = 'Class')
data_glom.fun.boer2n <- psmelt(glom.fun.boer2n)
data_glom.fun.boer2n$Class <- as.character(data_glom.fun.boer2n$Class)
```

```{r}
unique((data_glom.fun.boer2n$Class))
```

Top 6 classes
```{r}
data_glom.fun.nov.boer2.top6 <- subset(data_glom.fun.boer2n, Class == "Dothideomycetes"  | Class ==  "Agaricomycetes"  | Class ==   "Pezizomycetes"   | Class ==  "Sordariomycetes" | Class ==  
  "Eurotiomycetes"  | Class ==   "Leotiomycetes"  )
```

```{r}
unique((data_glom.fun.nov.boer2.top6$Class))
```

```{r}
fun.nov.boer <- ggplot(data_glom.fun.nov.boer2.top6,aes(Treatment,Abundance,color=Class)) + geom_boxplot() +
  scale_color_manual(values = c("indianred1", "lightsalmon","gray26","lightgreen", "lightblue1", "royalblue3")) + labs(y= "Relative Abundance") + theme_bw(base_size = 20) + theme(axis.text.x = element_text(angle = 90))
```

```{r}
fun.nov.boer
```

```{r}
figure3 <- ggarrange(fun.june.erle, fun.nov.erle, fun.june.boer, fun.nov.boer,
                    labels = c("A", "B","C","D"),
                    ncol = 2, nrow = 2)
```



```{r}
figure3
```

```{r}
figure3
ggsave("Figure3.png",width=12,height=8,dpi = 400)
```


