---
title: "Figure2"
author: "Andrew Dominguez"
date: "7/23/2020"
output: html_document
---

```{r}
#setwd("~/Manuscript.Figures")
```

```{r}
library(ape)
library(vegan)
library(plyr)
library(dplyr)
library(tidyr)
library(scales)
library(grid)
library(reshape2)
library(phyloseq)
library(magrittr)
library(ggplot2)
library(ggpubr)
library(data.table)
library(labdsv)
otu = read.table(file="../Data/LGasv16SUN3.otu_table.txt", header=T, sep='\t',row.names = 1)
head(otu)
dim(otu)
tax <- read.table(file="../Data/taxonomy.fix.16S.tsv", sep='\t', header=TRUE,row.names = 1)
head(tax)
dim(tax)
tax <- select(tax,-Confidence)
tax_filtered = separate(tax, Taxon, c("Kingdom","Phylum","Class","Order", "Family", "Genus","Species"), sep= ";", remove=TRUE)
head(tax_filtered)
taxmat <- as(as.matrix(tax_filtered),"matrix")
TAX = tax_table(taxmat)
otumat <- as(as.matrix(otu), "matrix")
mode(otumat) <- "numeric"
OTU = otu_table(otumat, taxa_are_rows = TRUE)
otumat
meta0 = read.table("../Data/Andrew16S_mappingfile.txt",
                  header=TRUE,row.names=1,
                  sep="\t",stringsAsFactors=FALSE)
head(meta0)
meta <- meta0[which(meta0$Owner %in% c("Andrew")),]
head(meta)
dim(meta)
sampleData <- sample_data(meta)
physeq = phyloseq(OTU,TAX,sampleData)
physeq
physeq.prune = prune_taxa(taxa_sums(physeq) > 0, physeq)
physeq
readcount = data.table(as(sample_data(physeq.prune), "data.frame"),
                 TotalReads = sample_sums(physeq.prune), 
                 keep.rownames = TRUE)
setnames(readcount, "rn", "SampleID")
readcount = readcount[order(readcount$TotalReads), c("SampleID", "TotalReads")]
head(readcount)
set.seed(711)
physeq.prune.rarefy = rarefy_even_depth(physeq.prune, sample.size = 37702, replace = FALSE, trimOTUs = TRUE)
physeq.prune.rarefy
bacteria <- subset_taxa(physeq.prune.rarefy, Kingdom == "Bacteria")
bacteria.con <- subset_samples(bacteria, Treatment == "Control")
bacteria.june <- subset_samples(bacteria, Date == "June_2017")
bacteria.nov <- subset_samples(bacteria, Date == "November_2017")
bacteria.june.control <- subset_samples(bacteria.june, Treatment == "Control")
bacteria.nov.control <- subset_samples(bacteria.nov, Treatment == "Control")
bacteria.june.erle <- subset_samples(bacteria.june, Grass == "ERLE")
bacteria.nov.erle <- subset_samples(bacteria.nov, Grass == "ERLE")
bacteria.june.boer <- subset_samples(bacteria.june, Grass == "BOER")
bacteria.nov.boer <- subset_samples(bacteria.nov, Grass == "BOER")
```

####group classes with less than 1% representation into one category -  ERLE June

##Make taxonomy table into a matrix
```{r}
tax.bac.june.erle <- as(tax_table(bacteria.june.erle),"matrix")
head(tax.bac.june.erle)
```

##Relabel NA as Unknown

```{r}
tax.bac.june.erle[is.na(tax.bac.june.erle)] <- "Unknown"
head(tax.bac.june.erle)
```

###Convert tax table back to phyloseq object and generate phyloseq object with new tax table
```{r}
TAX.bac.june.erle <- tax_table(tax.bac.june.erle)
```

```{r}
bac.june.erle2 <- phyloseq(sample_data(bacteria.june.erle),otu_table(bacteria.june.erle),TAX.bac.june.erle)
bac.june.erle2
```

```{r}
bac.june.erle0 = transform_sample_counts(bac.june.erle2, 
                                                      function(x) x / sum(x))
```

```{r}
glom.bac.june.erle2 <- tax_glom(bac.june.erle0,taxrank = 'Phylum')
data_glom.bac.june.erle2 <- psmelt(glom.bac.june.erle2)
data_glom.bac.june.erle2$Phylum <- as.character(data_glom.bac.june.erle2$Phylum)
```

```{r}
unique((data_glom.bac.june.erle2$Phylum))
```


Top 6 phyla

```{r}
data_glom.bac.june.erle2.top6 <- subset(data_glom.bac.june.erle2, Phylum == "Proteobacteria" | Phylum == "Actinobacteria" | Phylum == "Acidobacteria" | Phylum == "Chloroflexi" | Phylum == "Bacteroidetes" | Phylum == "Planctomycetes")
```

```{r}
unique(data_glom.bac.june.erle2.top6$Phylum)
```

```{r}
bac.june.erle <- ggplot(data_glom.bac.june.erle2.top6,aes(Treatment,Abundance,color=Phylum)) + geom_boxplot() +
  scale_color_manual(values = c("salmon","darkorange2", "lightgreen", "gray26", "maroon", "steelblue3")) + 
  theme_bw(base_size = 20) + labs(y= "Relative Abundance", x = "") + 
  ggtitle("A) ERLE Pre monsoon") + ylim(0, 0.4)
```

```{r}
bac.june.erle
```



#Stats comparing phylum abundance between treatments - Lovegrass June

```{r}
unique((data_glom.bac.june.erle2$Phylum))
```

```{r}
Acidobacteria <- subset(data_glom.bac.june.erle2, Phylum == "Acidobacteria")
Actinobacteria <- subset(data_glom.bac.june.erle2, Phylum == "Actinobacteria")
Bacteroidetes <- subset(data_glom.bac.june.erle2, Phylum == "Bacteroidetes")
Chloroflexi <- subset(data_glom.bac.june.erle2, Phylum == "Chloroflexi")
Planctomycetes <- subset(data_glom.bac.june.erle2, Phylum == "Planctomycetes")
Proteobacteria <- subset(data_glom.bac.june.erle2, Phylum == "Proteobacteria")
```

```{r}
Acidobacteria$Treatment <- as.factor(Acidobacteria$Treatment)
Actinobacteria$Treatment <- as.factor(Actinobacteria$Treatment)
Bacteroidetes$Treatment <- as.factor(Bacteroidetes$Treatment)
Chloroflexi$Treatment <- as.factor(Chloroflexi$Treatment)
Planctomycetes$Treatment <- as.factor(Planctomycetes$Treatment)
Proteobacteria$Treatment <- as.factor(Proteobacteria$Treatment)
```


```{r}
kw.1 <- kruskal.test(Abundance ~ Treatment,data = Acidobacteria)
kw.1
kw.2 <-kruskal.test(Abundance ~ Treatment,data = Actinobacteria)
kw.2
kw.3 <- kruskal.test(Abundance ~ Treatment,data = Bacteroidetes)
kw.3
kw.4 <- kruskal.test(Abundance ~ Treatment,data = Chloroflexi)
kw.4
kw.5 <- kruskal.test(Abundance ~ Treatment,data = Planctomycetes)
kw.5
kw.6 <- kruskal.test(Abundance ~ Treatment,data = Proteobacteria)
kw.6
```


####group classes with less than 1% representation into one category -  ERLE November

##Make taxonomy table into a matrix
```{r}
tax.bac.nov.erle <- as(tax_table(bacteria.nov.erle),"matrix")
head(tax.bac.nov.erle)
```

##Relabel NA as Unknown

```{r}
tax.bac.nov.erle[is.na(tax.bac.nov.erle)] <- "Unknown"
head(tax.bac.nov.erle)
```

###Convert tax table back to phyloseq object and generate phyloseq object with new tax table
```{r}
TAX.bac.nov.erle <- tax_table(tax.bac.nov.erle)
```

```{r}
bac.nov.erle2 <- phyloseq(sample_data(bacteria.nov.erle),otu_table(bacteria.nov.erle),TAX.bac.nov.erle)
bac.nov.erle2
```

```{r}
bac.nov.erle0 = transform_sample_counts(bac.nov.erle2, 
                                                      function(x) x / sum(x))
```

```{r}
glom.bac.nov.erle2 <- tax_glom(bac.nov.erle0,taxrank = 'Phylum')
data_glom.bac.nov.erle2 <- psmelt(glom.bac.nov.erle2)
data_glom.bac.nov.erle2$Phylum <- as.character(data_glom.bac.nov.erle2$Phylum)
```

```{r}
unique((data_glom.bac.nov.erle2$Phylum))
```

```{r}
data_glom.bac.nov.erle2.top6 <- subset(data_glom.bac.nov.erle2, Phylum == "Proteobacteria" | Phylum == "Actinobacteria" | Phylum == "Acidobacteria" | Phylum == "Chloroflexi" | Phylum == "Bacteroidetes" | Phylum == "Planctomycetes")
```

```{r}
unique(data_glom.bac.nov.erle2.top6$Phylum)
```


```{r}
bac.nov.erle <- ggplot(data_glom.bac.nov.erle2.top6,aes(Treatment,Abundance,color=Phylum)) + geom_boxplot() +
  scale_color_manual(values = c("salmon","darkorange2", "lightgreen", "gray26", "maroon", "steelblue3")) + 
  theme_bw(base_size = 20) + labs(y= "", x = "") + 
  ggtitle("B) ERLE Post monsoon") + ylim(0, 0.4)
```

```{r}
bac.nov.erle
```

```{r}
Pre_Post_Bac.treatment.plot = ggarrange(bac.june.erle, bac.nov.erle, ncol=2, common.legend = TRUE, legend = "right")#, labels = c("A", "B"))
Pre_Post_Bac.treatment.plot
```


#Stats comparing phylum abundance between treatments - Lovegrass November

```{r}
unique((data_glom.bac.nov.erle2$Phylum))
```

```{r}
Acidobacteria.nov<- subset(data_glom.bac.nov.erle2, Phylum == "Acidobacteria")
Actinobacteria.nov <- subset(data_glom.bac.nov.erle2, Phylum == "Actinobacteria")
Bacteroidetes.nov <- subset(data_glom.bac.nov.erle2, Phylum == "Bacteroidetes")
Chloroflexi.nov <- subset(data_glom.bac.nov.erle2, Phylum == "Chloroflexi")
Planctomycetes.nov <- subset(data_glom.bac.nov.erle2, Phylum == "Planctomycetes")
Proteobacteria.nov <- subset(data_glom.bac.nov.erle2, Phylum == "Proteobacteria")
```

```{r}
Acidobacteria.nov$Treatment <- as.factor(Acidobacteria.nov$Treatment)
Actinobacteria.nov$Treatment <- as.factor(Actinobacteria.nov$Treatment)
Bacteroidetes.nov$Treatment <- as.factor(Bacteroidetes.nov$Treatment)
Chloroflexi.nov$Treatment <- as.factor(Chloroflexi.nov$Treatment)
Planctomycetes.nov$Treatment <- as.factor(Planctomycetes.nov$Treatment)
Proteobacteria.nov$Treatment <- as.factor(Proteobacteria.nov$Treatment)
```


```{r}
kw.1 <- kruskal.test(Abundance ~ Treatment,data = Acidobacteria.nov)
kw.1
kw.2 <-kruskal.test(Abundance ~ Treatment,data = Actinobacteria.nov)
kw.2
kw.3 <- kruskal.test(Abundance ~ Treatment,data = Bacteroidetes.nov)
kw.3
kw.4 <- kruskal.test(Abundance ~ Treatment,data = Chloroflexi.nov)
kw.4
kw.5 <- kruskal.test(Abundance ~ Treatment,data = Planctomycetes.nov)
kw.5
kw.6 <- kruskal.test(Abundance ~ Treatment,data = Proteobacteria.nov)
kw.6
```


####group classes with less than 1% representation into one category -  BOER June

##Make taxonomy table into a matrix
```{r}
tax.bac.june.boer <- as(tax_table(bacteria.june.boer),"matrix")
head(tax.bac.june.boer)
```

##Relabel NA as Unknown

```{r}
tax.bac.june.boer[is.na(tax.bac.june.boer)] <- "Unknown"
head(tax.bac.june.boer)
```

###Convert tax table back to phyloseq object and generate phyloseq object with new tax table
```{r}
TAX.bac.june.boer <- tax_table(tax.bac.june.boer)
```

```{r}
bac.june.boer2 <- phyloseq(sample_data(bacteria.june.boer),otu_table(bacteria.june.boer),TAX.bac.june.boer)
bac.june.boer2
```

```{r}
bac.june.boer0 = transform_sample_counts(bac.june.boer2, 
                                                      function(x) x / sum(x))
```

```{r}
glom.bac.june.boer2 <- tax_glom(bac.june.boer0,taxrank = 'Phylum')
data_glom.bac.june.boer2 <- psmelt(glom.bac.june.boer2)
data_glom.bac.june.boer2$Phylum <- as.character(data_glom.bac.june.boer2$Phylum)
```

```{r}
unique((data_glom.bac.june.boer2$Phylum))
```

Top 6 phyla

```{r}
data_glom.bac.june.boer2.top6 <- subset(data_glom.bac.june.boer2, Phylum == "Proteobacteria" | Phylum == "Actinobacteria" | Phylum == "Acidobacteria" | Phylum == "Chloroflexi" | Phylum == "Bacteroidetes" | Phylum == "Planctomycetes")
```

```{r}
unique(data_glom.bac.june.boer2.top6$Phylum)
```


```{r}
bac.june.boer <- ggplot(data_glom.bac.june.boer2.top6,aes(Treatment,Abundance,color=Phylum)) + geom_boxplot() +
  scale_color_manual(values = c("salmon","darkorange2", "lightgreen", "gray26", "maroon", "steelblue3")) + 
  theme_bw(base_size = 20) + 
  labs(y= "Relative Abundance", x = "") + 
  ggtitle("C) BOER Pre monsoon") + ylim(0, 0.4)
```

```{r}
bac.june.boer
```

#Stats comparing phylum abundance between treatments - black grama June

```{r}
unique((data_glom.bac.june.boer2$Phylum))
```

```{r}
Acidobacteria.june <- subset(data_glom.bac.june.boer2, Phylum == "Acidobacteria")
Actinobacteria.june <- subset(data_glom.bac.june.boer2, Phylum == "Actinobacteria")
Bacteroidetes.june <- subset(data_glom.bac.june.boer2, Phylum == "Bacteroidetes")
Chloroflexi.june <- subset(data_glom.bac.june.boer2, Phylum == "Chloroflexi")
Planctomycetes.june <- subset(data_glom.bac.june.boer2, Phylum == "Planctomycetes")
Proteobacteria.june <- subset(data_glom.bac.june.boer2, Phylum == "Proteobacteria")
```

```{r}
Acidobacteria.june$Treatment <- as.factor(Acidobacteria.june$Treatment)
Actinobacteria.june$Treatment <- as.factor(Actinobacteria.june$Treatment)
Bacteroidetes.june$Treatment <- as.factor(Bacteroidetes.june$Treatment)
Chloroflexi.june$Treatment <- as.factor(Chloroflexi.june$Treatment)
Planctomycetes.june$Treatment <- as.factor(Planctomycetes.june$Treatment)
Proteobacteria.june$Treatment <- as.factor(Proteobacteria.june$Treatment)
```


```{r}
kw.1 <- kruskal.test(Abundance ~ Treatment,data = Acidobacteria.june)
kw.1
kw.2 <-kruskal.test(Abundance ~ Treatment,data = Actinobacteria.june)
kw.2
kw.3 <- kruskal.test(Abundance ~ Treatment,data = Bacteroidetes.june)
kw.3
kw.4 <- kruskal.test(Abundance ~ Treatment,data = Chloroflexi.june)
kw.4
kw.5 <- kruskal.test(Abundance ~ Treatment,data = Planctomycetes.june)
kw.5
kw.6 <- kruskal.test(Abundance ~ Treatment,data = Proteobacteria.june)
kw.6
```


####group classes with less than 1% representation into one category -  boer November

##Make taxonomy table into a matrix
```{r}
tax.bac.nov.boer <- as(tax_table(bacteria.nov.boer),"matrix")
head(tax.bac.nov.boer)
```

##Relabel NA as Unknown

```{r}
tax.bac.nov.boer[is.na(tax.bac.nov.boer)] <- "Unknown"
head(tax.bac.nov.boer)
```

###Convert tax table back to phyloseq object and generate phyloseq object with new tax table
```{r}
TAX.bac.nov.boer <- tax_table(tax.bac.nov.boer)
```

```{r}
bac.nov.boer2 <- phyloseq(sample_data(bacteria.nov.boer),otu_table(bacteria.nov.boer),TAX.bac.nov.boer)
bac.nov.boer2
```

```{r}
bac.nov.boer0 = transform_sample_counts(bac.nov.boer2, 
                                                      function(x) x / sum(x))
```

```{r}
glom.bac.nov.boer2 <- tax_glom(bac.nov.boer0,taxrank = 'Phylum')
data_glom.bac.nov.boer2 <- psmelt(glom.bac.nov.boer2)
data_glom.bac.nov.boer2$Phylum <- as.character(data_glom.bac.nov.boer2$Phylum)
```

```{r}
unique((data_glom.bac.nov.boer2$Phylum))
```

```{r}
data_glom.bac.nov.boer2.top6 <- subset(data_glom.bac.nov.boer2, Phylum == "Proteobacteria" | Phylum == "Actinobacteria" | Phylum == "Acidobacteria" | Phylum == "Chloroflexi" | Phylum == "Bacteroidetes" | Phylum == "Gemmatimonadetes")
```

```{r}
unique(data_glom.bac.nov.boer2.top6$Phylum)
```

```{r}
bac.nov.boer <- ggplot(data_glom.bac.nov.boer2.top6,aes(Treatment,Abundance,color=Phylum)) + geom_boxplot() +
  scale_color_manual(values = c("salmon","darkorange2", "lightgreen", "gray26", "hotpink2", "steelblue3")) + theme_bw(base_size = 20) + 
  labs(y= "", x = "") + 
  ggtitle("D) BOER Pre monsoon") + ylim(0, 0.4)
```

```{r}
bac.nov.boer
```

```{r}
Pre_Post_Fun.treatment.plot = ggarrange(bac.june.boer, bac.nov.boer, ncol=2, common.legend = TRUE, legend = "right")#, labels = c("C", "D"))
Pre_Post_Fun.treatment.plot
```

#Create figure2

```{r}
figure_2 = ggarrange(Pre_Post_Bac.treatment.plot, Pre_Post_Fun.treatment.plot, nrow = 2)
figure_2
```

##Save figure 2

```{r warning=FALSE}
pdf("../Figures/Figure_2_Pre_Post_0.4ylim.pdf", width = 12, height = 10 )
figure_2
dev.off()
```


```{r}
#figure2 <- ggarrange(bac.june.erle, bac.nov.erle, bac.june.boer, bac.nov.boer,
#                    labels = c("A", "B","C","D"),
#                    ncol = 2, nrow = 2)
```

```{r}
#figure2
```

##Save figure 2

```{r}
#figure2
#ggsave("Figure2.png",width=12,height=7,dpi = 400)
```

#Stats comparing phylum abundance between treatments - black grama June

```{r}
unique((data_glom.bac.nov.boer2$Phylum))
```

```{r}
Acidobacteria.nov <- subset(data_glom.bac.nov.boer2, Phylum == "Acidobacteria")
Actinobacteria.nov <- subset(data_glom.bac.nov.boer2, Phylum == "Actinobacteria")
Bacteroidetes.nov <- subset(data_glom.bac.nov.boer2, Phylum == "Bacteroidetes")
Chloroflexi.nov <- subset(data_glom.bac.nov.boer2, Phylum == "Chloroflexi")
Planctomycetes.nov <- subset(data_glom.bac.nov.boer2, Phylum == "Planctomycetes")
Proteobacteria.nov <- subset(data_glom.bac.nov.boer2, Phylum == "Proteobacteria")
```

```{r}
Acidobacteria.nov$Treatment <- as.factor(Acidobacteria.nov$Treatment)
Actinobacteria.nov$Treatment <- as.factor(Actinobacteria.nov$Treatment)
Bacteroidetes.nov$Treatment <- as.factor(Bacteroidetes.nov$Treatment)
Chloroflexi.nov$Treatment <- as.factor(Chloroflexi.nov$Treatment)
Planctomycetes.nov$Treatment <- as.factor(Planctomycetes.nov$Treatment)
Proteobacteria.nov$Treatment <- as.factor(Proteobacteria.nov$Treatment)
```


```{r}
kw.1 <- kruskal.test(Abundance ~ Treatment,data = Acidobacteria.nov)
kw.1
kw.2 <-kruskal.test(Abundance ~ Treatment,data = Actinobacteria.nov)
kw.2
kw.3 <- kruskal.test(Abundance ~ Treatment,data = Bacteroidetes.nov)
kw.3
kw.4 <- kruskal.test(Abundance ~ Treatment,data = Chloroflexi.nov)
kw.4
kw.5 <- kruskal.test(Abundance ~ Treatment,data = Planctomycetes.nov)
kw.5
kw.6 <- kruskal.test(Abundance ~ Treatment,data = Proteobacteria.nov)
kw.6
```