---
title: "Figure6_revised"
author: "Andrew Dominguez"
date: "8/10/2020"
output: html_document
---

```{r, setup, include=FALSE}
knitr::opts_knit$set(root.dir = '~/Downloads/Lovegrass_root_zone_microbiome/')
```

```{r}
library(ape)
library(vegan)
library(plyr)
library(dplyr)
library(tidyr)
library(scales)
library(grid)
library(reshape2)
library(phyloseq)
library(magrittr)
library(ggplot2)
library(ggpubr)
library(data.table)
library(labdsv)
otu = read.table(file="Data/LGasv16SUN3.otu_table.txt", header=T, sep='\t',row.names = 1)
head(otu)
dim(otu)
tax <- read.table(file="Data/taxonomy.fix.16S.tsv", sep='\t', header=TRUE,row.names = 1)
head(tax)
dim(tax)
tax <- select(tax,-Confidence)
tax_filtered = separate(tax, Taxon, c("Kingdom","Phylum","Class","Order", "Family", "Genus","Species"), sep= ";", remove=TRUE)
head(tax_filtered)
taxmat <- as(as.matrix(tax_filtered),"matrix")
TAX = tax_table(taxmat)
otumat <- as(as.matrix(otu), "matrix")
mode(otumat) <- "numeric"
OTU = otu_table(otumat, taxa_are_rows = TRUE)
otumat
meta0 = read.table("Data/Andrew16S_mappingfile.txt",
                  header=TRUE,row.names=1,
                  sep="\t",stringsAsFactors=FALSE)
head(meta0)
meta <- meta0[which(meta0$Owner %in% c("Andrew")),]
head(meta)
dim(meta)
sampleData <- sample_data(meta)
physeq = phyloseq(OTU,TAX,sampleData)
physeq
physeq.prune = prune_taxa(taxa_sums(physeq) > 0, physeq)
physeq
readcount = data.table(as(sample_data(physeq.prune), "data.frame"),
                 TotalReads = sample_sums(physeq.prune), 
                 keep.rownames = TRUE)
setnames(readcount, "rn", "SampleID")
readcount = readcount[order(readcount$TotalReads), c("SampleID", "TotalReads")]
head(readcount)
set.seed(711)
physeq.prune.rarefy = rarefy_even_depth(physeq.prune, sample.size = 37702, replace = FALSE, trimOTUs = TRUE)
physeq.prune.rarefy
bacteria <- subset_taxa(physeq.prune.rarefy, Kingdom == "Bacteria")
bacteria.con <- subset_samples(bacteria, Treatment == "Control")
bacteria.june <- subset_samples(bacteria, Date == "June_2017")
bacteria.nov <- subset_samples(bacteria, Date == "November_2017")
bacteria.june.control <- subset_samples(bacteria.june, Treatment == "Control")
bacteria.nov.control <- subset_samples(bacteria.nov, Treatment == "Control")
bacteria.june.erle <- subset_samples(bacteria.june, Grass == "ERLE")
bacteria.nov.erle <- subset_samples(bacteria.nov, Grass == "ERLE")
bacteria.june.boer <- subset_samples(bacteria.june, Grass == "BOER")
bacteria.nov.boer <- subset_samples(bacteria.nov, Grass == "BOER")
```

```{r}
bac.june <- as(sample_data(bacteria.june.control),"matrix")
bac.june <- data.frame(bac.june)
bac.june
```

###change phyloseq otu table to matrix

```{r}
bac.june.OTU <- as(otu_table(bacteria.june.control),"matrix")
head(bac.june.OTU)
```

###Transpose OTU table to show OTU's as columns, remove columns with 0's in OTU table

```{r}
bac.june.OTU <- t(bac.june.OTU)
bac.june.OTU2 <- bac.june.OTU[, colSums(bac.june.OTU != 0) > 0]
```


##Create table for grouping by grass 

```{r}
bac.june.grass <- subset(bac.june, select = "Grass")
head(bac.june.grass)
```

####Make Treatments numeric to make grouping compatable with indval command

```{r}
as.numeric(bac.june.grass$Grass)
```

```{r}
bac.grass.ind.j <- indval(bac.june.OTU2,bac.june.grass$Grass)
```

```{r}
head(bac.grass.ind.j)
```

###Create table with indicator species with p value of less than 0.05

```{r}
gr.june <- bac.grass.ind.j$maxcls[bac.grass.ind.j$pval <= 0.05]
iv.june <- bac.grass.ind.j$indcls[bac.grass.ind.j$pval <= 0.05]
pv.june <- bac.grass.ind.j$pval[bac.grass.ind.j$pval <= 0.05]
```

```{r}
bac.grass.ind.table.j <- data.frame(Grass=gr.june,indval=iv.june,pvalue=pv.june)
bac.grass.ind.table.j <- bac.grass.ind.table.j[order(bac.grass.ind.table.j$Grass, -bac.grass.ind.table.j$indval),]
```


###Change Grass from numbers to names

```{r}
bac.grass.ind.table.j$Grass <- gsub("1","BOER", bac.grass.ind.table.j$Grass)
bac.grass.ind.table.j$Grass <- gsub("2","ERLE", bac.grass.ind.table.j$Grass)
```

###Remove indicator species with an indicator value less than 0.9

```{r}
bac.grass.ind.table.j2 <- subset(bac.grass.ind.table.j,indval >= 0.9)
```


##Transpose indicator species OTU table to format for phyloseq object
```{r}
bac.june.OTU3 <- t(bac.june.OTU2)
```

```{r}
head(bac.june.OTU3)
```


###Add otu table to indicator species table

```{r}
bac.indic.otu.grass.j = bac.june.OTU3[row.names(bac.june.OTU3) %in% row.names(bac.grass.ind.table.j2),]
bac.indic.otumat.grass.j <- as(as.matrix(bac.indic.otu.grass.j), "matrix")
bac.grass.indic.OTU.j = otu_table(bac.indic.otumat.grass.j, taxa_are_rows = TRUE)
```

```{r}
bac.physeq.grass.june <- phyloseq(bac.grass.indic.OTU.j,TAX,sampleData)
bac.physeq.grass.june
```

```{r}
bac.tax.grass.june <- as(tax_table(bac.physeq.grass.june),"matrix")
```

```{r}
bac.tax.grass.june[is.na(bac.tax.grass.june)] <- "Unknown"
head(bac.tax.grass.june)
```

```{r}
bac.tax.grass.june <- tax_table(bac.tax.grass.june)
```

```{r}
bac.physeq.grass.june2 <- phyloseq(otu_table(bac.physeq.grass.june),bac.tax.grass.june,sample_data(bac.physeq.grass.june))
```


##Get the average abundance of each indicator for each grass

```{r}
bac.avg.june.con <- merge_samples(bac.physeq.grass.june2, "Grass")
sample_data(bac.avg.june.con)$Grass <- factor(sample_names(bac.avg.june.con))
```

```{r}
bac.avg.june.con
```

```{r}
bac.avg.june.OTU <- as(otu_table(bac.avg.june.con),"matrix")
head(bac.avg.june.OTU)
```

```{r}
bac.avg.june.TAX <- as(tax_table(bac.avg.june.con),"matrix")
head(bac.avg.june.TAX)
```

```{r}
bac.avg.june.Sample <- as(sample_data(bac.avg.june.con),"matrix")
head(bac.avg.june.Sample)
```

##Edit column in sample data

```{r}
bac.avg.june.Sample <- gsub("BOER", "BOER.June", bac.avg.june.Sample)
bac.avg.june.Sample <- gsub("ERLE", "ERLE.June", bac.avg.june.Sample)
```

```{r}
bac.avg.june.Sample <- data.frame(bac.avg.june.Sample)
```


```{r}
bac.avg.june.Sample.edit <- sample_data(bac.avg.june.Sample)
```

###Create new phylsoeq object with edited sample data

```{r}
bac.avg.June.indicators <- phyloseq(tax_table(bac.avg.june.con), otu_table(bac.avg.june.con), bac.avg.june.Sample.edit)
bac.avg.June.indicators
```



##Subset sample data to look at BOER and ERLE bacterial communities from November 

```{r}
bac.nov <- as(sample_data(bacteria.nov.control),"matrix")
bac.nov <- data.frame(bac.nov)
bac.nov
```

###Make phyloseq object into a matrix


```{r}
bac.nov.OTU <- as(otu_table(bacteria.nov.control),"matrix")
head(bac.nov.OTU)
```

###Transpose OTU table to show OTU's as columns, remove columns with 0's in OTU table

```{r}
bac.nov.OTU <- t(bac.nov.OTU)
dim(bac.nov.OTU)
bac.nov.OTU2 <- bac.nov.OTU[, colSums(bac.nov.OTU != 0) > 0]
dim(bac.nov.OTU2)
```


##Create table for grouping by grass 

```{r}
bac.nov.grass <- subset(bac.nov, select = "Grass")
head(bac.nov.grass)
```

####Make Treatments numeric to make grouping compatable with indval command

```{r}
as.numeric(bac.nov.grass$Grass)
```

```{r}
bac.grass.ind <- indval(bac.nov.OTU2,bac.nov.grass$Grass)
```

```{r}
head(bac.grass.ind)
```

###Create table with indicator species with p value of less than 0.05

```{r}
gr.nov <- bac.grass.ind$maxcls[bac.grass.ind$pval <= 0.05]
iv.nov <- bac.grass.ind$indcls[bac.grass.ind$pval <= 0.05]
pv.nov <- bac.grass.ind$pval[bac.grass.ind$pval <= 0.05]
```

```{r}
bac.grass.ind.table <- data.frame(Grass=gr.nov,indval=iv.nov,pvalue=pv.nov)
bac.grass.ind.table <- bac.grass.ind.table[order(bac.grass.ind.table$Grass, -bac.grass.ind.table$indval),]
```




###Change Grass from numbers to names

```{r}
bac.grass.ind.table$Grass <- gsub("1","BOER", bac.grass.ind.table$Grass)
bac.grass.ind.table$Grass <- gsub("2","ERLE", bac.grass.ind.table$Grass)
```

###Remove indicator species with an indicator value less than 0.9

```{r}
bac.grass.ind.table2 <- subset(bac.grass.ind.table,indval >= 0.9)
```


##Transpose indicator species OTU table to format for phyloseq object
```{r}
bac.nov.OTU3 <- t(bac.nov.OTU2)
```

```{r}
head(bac.nov.OTU3)
```


###Add otu table to indicator species table

```{r}
bac.indic.otu.grass = bac.nov.OTU3[row.names(bac.nov.OTU3) %in% row.names(bac.grass.ind.table2),]
bac.indic.otumat.grass <- as(as.matrix(bac.indic.otu.grass), "matrix")
bac.grass.indic.OTU = otu_table(bac.indic.otumat.grass, taxa_are_rows = TRUE)
```




```{r}
bac.physeq.grass.nov <- phyloseq(bac.grass.indic.OTU,TAX,sampleData)
bac.physeq.grass.nov
```


```{r}
bac.tax.grass.nov <- as(tax_table(bac.physeq.grass.nov),"matrix")
```

```{r}
bac.tax.grass.nov[is.na(bac.tax.grass.nov)] <- "Unknown"
head(bac.tax.grass.nov)
```

```{r}
bac.tax.grass.nov <- tax_table(bac.tax.grass.nov)
```

```{r}
bac.physeq.grass.nov2 <- phyloseq(otu_table(bac.physeq.grass.nov),bac.tax.grass.nov,sample_data(bac.physeq.grass.nov))
```



##Get the average abundance of each indicator for each grass - November

```{r}
bac.avg.nov.con <- merge_samples(bac.physeq.grass.nov2, "Grass")
sample_data(bac.avg.nov.con)$Grass <- factor(sample_names(bac.avg.nov.con))
```

```{r}
bac.avg.nov.con
```

```{r}
bac.avg.nov.OTU <- as(otu_table(bac.avg.nov.con),"matrix")
head(bac.avg.nov.OTU)
```

```{r}
bac.avg.nov.TAX <- as(tax_table(bac.avg.nov.con),"matrix")
head(bac.avg.nov.TAX)
```

```{r}
bac.avg.nov.Sample <- as(sample_data(bac.avg.nov.con),"matrix")
head(bac.avg.nov.Sample)
```

##Edit column in sample data

```{r}
bac.avg.nov.Sample <- gsub("BOER", "BOER.Nov", bac.avg.nov.Sample)
bac.avg.nov.Sample <- gsub("ERLE", "ERLE.Nov", bac.avg.nov.Sample)
```

```{r}
bac.avg.nov.Sample <- data.frame(bac.avg.nov.Sample)
```


```{r}
bac.avg.nov.Sample.edit <- sample_data(bac.avg.nov.Sample)
```

###Create new phylsoeq object with edited sample data

```{r}
bac.avg.nov.indicators <- phyloseq(tax_table(bac.avg.nov.con), otu_table(bac.avg.nov.con), bac.avg.nov.Sample.edit)
bac.avg.nov.indicators
```


##Creating a heatmap of average Taxonomic abundance



```{r}
bac.avg.June.indicators
```

```{r}
bac.avg.June.indicators.otu <- as(otu_table(bac.avg.June.indicators),"matrix")
bac.avg.June.indicators.otu
```

```{r}
rownames(bac.avg.June.indicators.otu) <- c("BOER.June","ERLE.June")
bac.avg.June.indicators.otu
```

```{r}
bac.avg.June.indicators.otu.2 <- t(bac.avg.June.indicators.otu)
```

```{r}
bac.avg.June.indicators.otu.3 <- otu_table(bac.avg.June.indicators.otu.2,taxa_are_rows = TRUE)
```



```{r}
bac.avg.June.indicators.sample <- as(sample_data(bac.avg.June.indicators),"matrix")
bac.avg.June.indicators.sample
```

```{r}
rownames(bac.avg.June.indicators.sample) <- c("BOER.June","ERLE.June")
bac.avg.June.indicators.sample
```

```{r}
bac.avg.June.indicators.sample <- data.frame(bac.avg.June.indicators.sample)
```


```{r}
bac.avg.June.indicators.Sample <- sample_data(bac.avg.June.indicators.sample)
head(bac.avg.June.indicators.Sample)
```



```{r}
bac.avg.June.indicators2 <- phyloseq(bac.avg.June.indicators.otu.3,bac.avg.June.indicators.Sample,tax_table(bac.avg.June.indicators))
bac.avg.June.indicators2
```




```{r}
bac.avg.nov.indicators.otu <- as(otu_table(bac.avg.nov.indicators),"matrix")
bac.avg.nov.indicators.otu
```

```{r}
rownames(bac.avg.nov.indicators.otu) <- c("BOER.Nov","ERLE.Nov")
bac.avg.nov.indicators.otu
```

```{r}
bac.avg.nov.indicators.otu.2 <- t(bac.avg.nov.indicators.otu)
```

```{r}
bac.avg.nov.indicators.otu.3 <- otu_table(bac.avg.nov.indicators.otu.2,taxa_are_rows = TRUE)
```



```{r}
bac.avg.nov.indicators.sample <- as(sample_data(bac.avg.nov.indicators),"matrix")
bac.avg.nov.indicators.sample
```

```{r}
rownames(bac.avg.nov.indicators.sample) <- c("BOER.Nov","ERLE.Nov")
bac.avg.nov.indicators.sample
```

```{r}
bac.avg.nov.indicators.sample <- data.frame(bac.avg.nov.indicators.sample)
```


```{r}
bac.avg.nov.indicators.Sample <- sample_data(bac.avg.nov.indicators.sample)
head(bac.avg.nov.indicators.Sample)
```



```{r}
bac.avg.nov.indicators2 <- phyloseq(bac.avg.nov.indicators.otu.3,bac.avg.nov.indicators.Sample,tax_table(bac.avg.nov.indicators))
bac.avg.nov.indicators2
```

```{r}
bac.avg.control.indic <- merge_phyloseq(bac.avg.June.indicators2,bac.avg.nov.indicators2)
bac.avg.control.indic
```


##Prune taxa

```{r}
bac.avg.control.indic.25 <- prune_taxa(names(sort(taxa_sums(bac.avg.control.indic),TRUE)[1:25]), bac.avg.control.indic)
```

```{r}
sample.25 <- as(sample_data(bac.avg.control.indic.25),"data.frame")
```

```{r}
sample.25$Grass <- factor(sample.25$Grass, levels = c("BOER.June", "ERLE.June", "BOER.Nov", "ERLE.Nov"))
```

```{r}
sample.25 <- sample_data(sample.25)
```

```{r}
bac.avg.control.indic.25.ordered <- phyloseq(tax_table(bac.avg.control.indic.25), otu_table(bac.avg.control.indic.25),sample.25)
```






```{r}
heatmap.con.bac <- plot_heatmap(bac.avg.control.indic.25.ordered, sample.label="Grass",low = "lightyellow2", na.value = "white", high = "steelblue4", sample.order = sample_names(bac.avg.control.indic.25.ordered)) + theme_bw(base_size = 20) + ylab("ASV")
```

```{r}
heatmap.con.bac
```


#Fungi

```{r}
otu = read.table(file="Data/FungiAD.otu_table.txt", header=T, sep='\t',row.names = 1)
head(otu)
dim(otu)

tax <- read.table(file="Data/FungiAD.ASVs.taxonomy.fix.txt", sep='\t', header=TRUE,row.names = 1)
head(tax)

dim(tax)

taxmat <- as(tax,"matrix")
head(taxmat)

TAX = tax_table(taxmat)

otumat <- as(as.matrix(otu), "matrix")
mode(otumat) <- "numeric"
OTU = otu_table(otumat, taxa_are_rows = TRUE)

otumat

meta0 = read.table("Data/Andrew_ITS.mapping_file.txt",
                  header=TRUE,row.names=1,
                  sep="\t",stringsAsFactors=FALSE)
meta0

sampleData <- sample_data(meta0)


physeq = phyloseq(OTU,TAX,sampleData)



physeq


physeq.prune = prune_taxa(taxa_sums(physeq) > 0, physeq)
physeq

readcount = data.table(as(sample_data(physeq.prune), "data.frame"),
                 TotalReads = sample_sums(physeq.prune), 
                 keep.rownames = TRUE)
setnames(readcount, "rn", "SampleID")


readcount = readcount[order(readcount$TotalReads), c("SampleID", "TotalReads")]
head(readcount)

set.seed(711)
physeq.prune.rarefy = rarefy_even_depth(physeq.prune, sample.size = 4941, replace = FALSE, trimOTUs = TRUE)
physeq.prune.rarefy

physeq.prune.rarefy.fun <- subset_taxa(physeq.prune.rarefy,Kingdom == "Fungi")
physeq.prune.rarefy.fun

fun.con <- subset_samples(physeq.prune.rarefy.fun, Treatment == "Control")
fun.june <- subset_samples(physeq.prune.rarefy.fun, Date == "June_2017")
fun.nov <- subset_samples(physeq.prune.rarefy.fun, Date == "November_2017")
fun.june.control <- subset_samples(fun.june, Treatment == "Control")
fun.nov.control <- subset_samples(fun.nov, Treatment == "Control")
fun.june.erle <- subset_samples(fun.june, Grass == "ERLE")
fun.june.boer <- subset_samples(fun.june, Grass == "BOER")
fun.nov.erle <- subset_samples(fun.nov, Grass == "ERLE")
fun.nov.boer <- subset_samples(fun.nov, Grass == "BOER")
```


###Indicator species analysis using labdsv package - Comparing BOER and ERLE fungal communities - Control - June 2017

```{r}
fun.june <- as(sample_data(fun.june.control),"matrix")
fun.june <- data.frame(fun.june)
fun.june
```

###change phyloseq otu table to matrix

```{r}
fun.june.OTU <- as(otu_table(fun.june.control),"matrix")
head(fun.june.OTU)
```


###Transpose OTU table to show OTU's as columns

```{r}
fun.june.OTU <- t(fun.june.OTU)
```

###Remove columns with 0's in OTU table

```{r}
fun.june.OTU2 <- fun.june.OTU[, colSums(fun.june.OTU != 0) > 0]
```

##Create table for grouping by grass 

```{r}
fun.june.grass <- subset(fun.june, select = "Grass")
head(fun.june.grass)
```

####Make Treatments numeric to make grouping compatable with indval command

```{r}
as.numeric(fun.june.grass$Grass)
```

```{r}
grass.fun.ind.j <- indval(fun.june.OTU2,fun.june.grass$Grass)
```


###Create table with indicator species with p value of less than 0.05

```{r}
gr.june.fun <- grass.fun.ind.j$maxcls[grass.fun.ind.j$pval <= 0.05]
iv.june.fun <- grass.fun.ind.j$indcls[grass.fun.ind.j$pval <= 0.05]
pv.june.fun <- grass.fun.ind.j$pval[grass.fun.ind.j$pval <= 0.05]
```

```{r}
grass.fun.ind.table.j <- data.frame(Grass=gr.june.fun,indval=iv.june.fun,pvalue=pv.june.fun)
grass.fun.ind.table.j <- grass.fun.ind.table.j[order(grass.fun.ind.table.j$Grass, -grass.fun.ind.table.j$indval),]
```


###Change Grass from numbers to names

```{r}
grass.fun.ind.table.j$Grass <- gsub("1","BOER", grass.fun.ind.table.j$Grass)
grass.fun.ind.table.j$Grass <- gsub("2","ERLE", grass.fun.ind.table.j$Grass)
```

###Remove indicator species with an indicator value less than 0.8

```{r}
grass.fun.ind.table.j2 <- subset(grass.fun.ind.table.j,indval >= 0.8)
```

##Transpose indicator species OTU table to format for phyloseq object
```{r}
fun.june.OTU3 <- t(fun.june.OTU2)
```

```{r}
head(fun.june.OTU3)
```


###Add otu table to indicator species table

```{r}
indic.fun.otu.grass.j = fun.june.OTU3[row.names(fun.june.OTU3) %in% row.names(grass.fun.ind.table.j2),]
indic.fun.otumat.grass.j <- as(as.matrix(indic.fun.otu.grass.j), "matrix")
grass.fun.indic.OTU.j = otu_table(indic.fun.otumat.grass.j, taxa_are_rows = TRUE)
```

```{r}
physeq.fun.grass.june <- phyloseq(grass.fun.indic.OTU.j,TAX,sampleData)
physeq.fun.grass.june
```

```{r}
physeq.fun.grass.june <- subset_taxa(physeq.fun.grass.june, Kingdom == "Fungi")
physeq.fun.grass.june
```

```{r}
tax.grass.j <- as(tax_table(physeq.fun.grass.june),"matrix")
```

```{r}
tax.grass.j[is.na(tax.grass.j)] <- "Unknown"
head(tax.grass.j)
```

```{r}
tax.grass.j <- tax_table(tax.grass.j)
```

```{r}
physeq.fun.grass.june2 <- phyloseq(otu_table(physeq.fun.grass.june),tax.grass.j,sample_data(physeq.fun.grass.june))
```







###Indicator species analysis using labdsv package - Comparing BOER and ERLE fungal communities - Control - November 2017


```{r}
fun.nov <- as(sample_data(fun.nov.control),"matrix")
fun.nov <- data.frame(fun.nov)
fun.nov
```

###Convert OTU table to matrix

```{r}
fun.nov.OTU <- as(otu_table(fun.nov.control),"matrix")
head(fun.nov.OTU)
```

###Transpose OTU table to show OTU's as columns

```{r}
fun.nov.OTU <- t(fun.nov.OTU)
dim(fun.nov.OTU)
```

###Remove columns with 0's in OTU table

```{r}
fun.nov.OTU2 <- fun.nov.OTU[, colSums(fun.nov.OTU != 0) > 0]
dim(fun.nov.OTU2)
```

##Create table for grouping by grass 

```{r}
fun.nov.grass <- subset(fun.nov, select = "Grass")
head(fun.nov.grass)
```

####Make Treatments numeric to make grouping compatable with indval command

```{r}
as.numeric(fun.nov.grass$Grass)
```

```{r}
grass.ind.fun <- indval(fun.nov.OTU2,fun.nov.grass$Grass)
```


###Create table with indicator species with p value of less than 0.05

```{r}
gr <- grass.ind.fun$maxcls[grass.ind.fun$pval <= 0.05]
iv <- grass.ind.fun$indcls[grass.ind.fun$pval <= 0.05]
pv <- grass.ind.fun$pval[grass.ind.fun$pval <= 0.05]
```

```{r}
grass.ind.table.fun <- data.frame(Grass=gr,indval=iv,pvalue=pv)
grass.ind.table.fun <- grass.ind.table.fun[order(grass.ind.table.fun$Grass, -grass.ind.table.fun$indval),]
```




```{r}
fun.OTU3 <- t(fun.nov.OTU2)
```

```{r}
head(fun.OTU3)
```

```{r}
grass.ind.table.fun$Grass <- gsub("1","BOER", grass.ind.table.fun$Grass)
grass.ind.table.fun$Grass <- gsub("2","ERLE", grass.ind.table.fun$Grass)
```

```{r}
grass.ind.table.fun2 <- subset(grass.ind.table.fun,indval >= 0.8)
```

###Add otu table to indicator species table

```{r}
indic.otus.filtered = fun.OTU3[row.names(fun.OTU3) %in% row.names(grass.ind.table.fun2),]
indic.otumat <- as(as.matrix(indic.otus.filtered), "matrix")
indic.OTU = otu_table(indic.otumat, taxa_are_rows = TRUE)
```

###New phyloseq object

```{r}
physeq.fun.indic <- phyloseq(indic.OTU,TAX,sampleData)
physeq.fun.indic
```

```{r}
tax.grass.nov.f <- as(tax_table(physeq.fun.indic),"matrix")
```

```{r}
tax.grass.nov.f[is.na(tax.grass.nov.f)] <- "Unknown"
head(tax.grass.nov.f)
```

```{r}
tax.grass.nov.f <- tax_table(tax.grass.nov.f)
```

```{r}
physeq.fun.indic2 <- phyloseq(otu_table(physeq.fun.indic),tax.grass.nov.f,sample_data(physeq.fun.indic))
```




Finding average abundance of indicators



##Get the average abundance of each indicator for each grass - June

```{r}
avg.june.con <- merge_samples(physeq.fun.grass.june2, "Grass")
sample_data(avg.june.con)$Grass <- factor(sample_names(avg.june.con))
```

```{r}
avg.june.con
```

```{r}
avg.june.OTU <- as(otu_table(avg.june.con),"matrix")
head(avg.june.OTU)
```

```{r}
avg.june.TAX <- as(tax_table(avg.june.con),"matrix")
head(avg.june.TAX)
```

```{r}
avg.june.Sample <- as(sample_data(avg.june.con),"matrix")
head(avg.june.Sample)
```

##Edit column in sample data

```{r}
avg.june.Sample <- gsub("BOER", "BOER.June", avg.june.Sample)
avg.june.Sample <- gsub("ERLE", "ERLE.June", avg.june.Sample)
```

```{r}
avg.june.Sample <- data.frame(avg.june.Sample)
```


```{r}
avg.june.Sample.edit <- sample_data(avg.june.Sample)
```

###Create new phylsoeq object with edited sample data

```{r}
avg.June.indicators <- phyloseq(tax_table(avg.june.con), otu_table(avg.june.con), avg.june.Sample.edit)
avg.June.indicators
```

##Get the average abundance of each indicator for each grass - November

```{r}
avg.nov.con <- merge_samples(physeq.fun.indic2, "Grass")
sample_data(avg.nov.con)$Grass <- factor(sample_names(avg.nov.con))
```

```{r}
avg.nov.con
```

```{r}
avg.nov.OTU <- as(otu_table(avg.nov.con),"matrix")
head(avg.nov.OTU)
```

```{r}
avg.nov.TAX <- as(tax_table(avg.nov.con),"matrix")
head(avg.nov.TAX)
```

```{r}
avg.nov.Sample <- as(sample_data(avg.nov.con),"matrix")
head(avg.nov.Sample)
```

##Edit column in sample data

```{r}
avg.nov.Sample <- gsub("BOER", "BOER.Nov", avg.nov.Sample)
avg.nov.Sample <- gsub("ERLE", "ERLE.Nov", avg.nov.Sample)
```

```{r}
avg.nov.Sample <- data.frame(avg.nov.Sample)
```


```{r}
avg.nov.Sample.edit <- sample_data(avg.nov.Sample)
```

###Create new phylsoeq object with edited sample data

```{r}
avg.nov.indicators <- phyloseq(tax_table(avg.nov.con), otu_table(avg.nov.con), avg.nov.Sample.edit)
avg.nov.indicators
```


##Creating a heatmap of average Taxonomic abundance



```{r}
avg.June.indicators
```

```{r}
avg.June.indicators.otu <- as(otu_table(avg.June.indicators),"matrix")
avg.June.indicators.otu
```

```{r}
rownames(avg.June.indicators.otu) <- c("BOER.June","ERLE.June")
avg.June.indicators.otu
```

```{r}
avg.June.indicators.otu.2 <- t(avg.June.indicators.otu)
```

```{r}
avg.June.indicators.otu.3 <- otu_table(avg.June.indicators.otu.2,taxa_are_rows = TRUE)
```



```{r}
avg.June.indicators.sample <- as(sample_data(avg.June.indicators),"matrix")
avg.June.indicators.sample
```

```{r}
rownames(avg.June.indicators.sample) <- c("BOER.June","ERLE.June")
avg.June.indicators.sample
```

```{r}
avg.June.indicators.sample <- data.frame(avg.June.indicators.sample)
```


```{r}
avg.June.indicators.Sample <- sample_data(avg.June.indicators.sample)
head(avg.June.indicators.Sample)
```



```{r}
avg.June.indicators2 <- phyloseq(avg.June.indicators.otu.3,avg.June.indicators.Sample,tax_table(avg.June.indicators))
avg.June.indicators2
```




```{r}
avg.nov.indicators.otu <- as(otu_table(avg.nov.indicators),"matrix")
avg.nov.indicators.otu
```

```{r}
rownames(avg.nov.indicators.otu) <- c("BOER.Nov","ERLE.Nov")
avg.nov.indicators.otu
```

```{r}
avg.nov.indicators.otu.2 <- t(avg.nov.indicators.otu)
```

```{r}
avg.nov.indicators.otu.3 <- otu_table(avg.nov.indicators.otu.2,taxa_are_rows = TRUE)
```



```{r}
avg.nov.indicators.sample <- as(sample_data(avg.nov.indicators),"matrix")
avg.nov.indicators.sample
```

```{r}
rownames(avg.nov.indicators.sample) <- c("BOER.Nov","ERLE.Nov")
avg.nov.indicators.sample
```

```{r}
avg.nov.indicators.sample <- data.frame(avg.nov.indicators.sample)
```


```{r}
avg.nov.indicators.Sample <- sample_data(avg.nov.indicators.sample)
head(avg.nov.indicators.Sample)
```



```{r}
avg.nov.indicators2 <- phyloseq(avg.nov.indicators.otu.3,avg.nov.indicators.Sample,tax_table(avg.nov.indicators))
avg.nov.indicators2
```

```{r}
avg.control.indic <- merge_phyloseq(avg.June.indicators2,avg.nov.indicators2)
avg.control.indic
```

```{r}
sample.fun <- as(sample_data(avg.control.indic),"data.frame")
```

```{r}
sample.fun$Grass <- factor(sample.fun$Grass, levels = c("BOER.June", "ERLE.June", "BOER.Nov", "ERLE.Nov"))
```

```{r}
sample.fun <- sample_data(sample.fun)
```

```{r}
avg.control.indic.ordered <- phyloseq(tax_table(avg.control.indic), otu_table(avg.control.indic),sample.fun)
```


```{r}
heatmap.fun.control <- plot_heatmap(avg.control.indic.ordered, sample.label="Grass",low = "lightyellow2", na.value = "white", high = "steelblue4", sample.order = sample_names(avg.control.indic.ordered)) + theme_bw(base_size = 20) + ylab("ASV")
```

```{r}
heatmap.fun.control
```


```{r}
figure6 <- ggarrange(heatmap.con.bac, heatmap.fun.control,
                    labels = c("A", "B"),
                    ncol = 1, nrow = 2)
```



```{r}
figure6
```



```{r}
setwd("~/Documents/Lovegrass_amptk.qiime2/Manuscript.Figures/")
figure6
ggsave("Figure6.png",width=12,height=10.5,dpi = 400)
```

